---
title: Does the gender and ethnicity of New College students influence their experience
  with math classes?
author: "Adriana Souza, Lydia LaSeur, Roger Filmyer"
date: "November 12th, 2017"
bibliography: citations.bibtex
output:
  html_notebook:
    highlight: tango
    mathjax: null
    number_sections: yes
    theme: spacelab
    toc: yes
    toc_float: yes
---

```{r setup, include=FALSE}
# Loading packages we will be using
library(survey)
library(srvyr)
library(psych)
library(shiny)
library(plyr)
library(dplyr)
library(ggplot2)
library(tibble)
library(reshape2)
library(tidyr)
library(stringi)
library(likert)

```


# Overview and motivation

This is a report created for Professor Chris Kottke's survey. Goals of the survey were to get more information about the students in order to address the lack of gender diversity in the math AOC. Dr. Kottke wanted to get a sense of how the students feel and test the incidence of things like belonging uncertainty, impostor syndrome, and stereotype threat at New College of Florida.

The questions had the following goals: 

(1) Gauging interest in mathematics
(2) Measuring belonging uncertainty
(3) Measuring confidence levels
(4) Stereotype threat

Conditioned on the self-reported gender and ethinicity.

## Survey information

The population consists of New College students exclusively, given that only respondents with an *@ncf.edu* email address were allowed to reply. 

+ New College has 861 students (as of Fall 2016) and the survey had a total of 264 responses which are all complete.

+ Responders: 60% female, 28.3% male, 11.7% non-binary.

+ The data was de-identified for the purpose of this study so no IRB approval was required. 

## Data

Likert-type responses were chosen due to being a popular psychometric item scoring scheme when trying to quantify people’s opinions on different issues. 

The problem with Likert-type scales and ordinal responses is how to choose the appropriate statistical treatment of the data. If the data is ordinal, then non-parametric statistics are typically considered the most appropriate option for analysis. If the data is interval, then parametric statistics can be used. 

To avoid possible misinterpretation, we took care in analyzing how each variable and question were coded. Additionally, each question has corresponding visualizations that illustrate the relationships more clearly. 

### Gender

One of the biggest questions we had with our survey data was the question of gender identity. Traditionally, studies looking at gender differences versus educational attainment have assumed a strict male/female gender binary.
Even more recent studies have taken into account nonbinary gender as a survey question, but did not include the relatively small number of respondents identifying as nonbinary in their analysis. [@clancy]
We found neither of these approaches satisfactory. We, along with Dr. Kottke, felt it irresponsible to assume a gender binary in our survey questioning. And while the analytical shortcut of ignoring nonbinary participants might have surved Clancy et. al.'s purposes, given their low number and proportion of nonbinary respondents (n, x%),  we found a much larger proportion of our survey sample identifying as nonbinary (n, x%), a group that we can not ignore for statistical reasons as well as moral reasons.

This forced us to question what exactly we wanted to measure as a predictor variable: Gender identity, gender conformity, masculinity, or femininity.
We ended up focusing on the role of masculinity, given that articles with queer-focused and intersectional prespectives specifically talk about the "masculine nature of both math and sciences"[@yodermattheis 22], or the "male superiority myth"[@leyva 399]. Our issue appears to be one of masculinity specifically.

WIth this in mind, instead of looking at gender identity, we looked at masculinity as a predictor. We transformed our responses to the gender identity question into a binary variable of whether the respondent self-identified as male, or not. Only responses where a survey participant checked the box indicating "Male" were coded as "yes" for the variable; all "Female" box checks or "Other" answers (including if the subject indicated they were a trans man, but did not check the "Male" box), were coded as "no". This is an approach we had not found addressed in literature, but with substantially higher nonbinary participation on a survey that was not specifically targeted at nonbinary or transgender individuals, we found ourselves facing relatively novel circumstances.

### Issues

Likert scales may be subject to distortion from several causes. 

First, Likert scales are arbitrary; the value assigned to an item has no objective numerical basis, either in terms of measure theory or scale (from which a distance metric can be determined). The value assigned to each Likert item is determined by who designed the survey.

The second major problem is whether the "distance" between each Likert item is equivalent. A good Likert scale will present a symmetry of categories about a midpoint with clearly defined linguistic qualifiers.

- **Non-response bias**

The phenomenon that the required information is not obtained from the people selected in the sample.

- **Social Desirability and acquiescence bias**

Respondents may avoid using extreme response categories out of a desire of being perceived as having extremist views

Agree with statements as presented ...


- **Sample size and power** 
The probability of not getting false positives is affected by three factors:

+ **Sample size (n)** The greater the sample size, the greater the power.  In our case, Other things being equal, the number of responses (264) represents 31% of currently enrolled students at New College. 

+ **Significance level ($\alpha$)** The higher the significance level, the higher the power of the test. Increasing the significance level reduces the region of acceptance. As a result, we are more likely to reject the null hypothesis; i.e., we are less likely to accept the null hypothesis when it is false, or making a Type II error. This increases the statistical power of the test.

+ **The "true" value of the parameter being tested** The greater the difference between the "true" value of a parameter and the value specified in the null hypothesis, the greater the power of the test. That is, the greater the effect size, the greater the power of the test.

### Corrections

- Using weighted averages:

- Design questions with students' sensitivity in mind; e.g. asking directly what their assessment of their own levels of confidence may not yield usable data due to issues mentioned above

- Having a scale design with balanced keying (an equal number of positive and negative statements regarding each position or issue in question) can mitigate the random error caused by acquiescence bias. Defensive, central tendency, and social desirability biases are somewhat more problematic and were not explicitly addressed in this analysis.

- Lastly, using sliders instead of the typical five-level format would yielf a continuous response variable which would expand the number of tests that could be used for analysis.

# Analysis

+ Non-parametric rank-based inference such as the median, the Mann-Whitney U test, or the Kruskal Wallis test. 

+ But if we have a well-defined likert scale, we might still be able to get useful results with standard statistical summaries and inference as well (though Melissa is not sure whether the assumptions for standard linear regression would be met).

+  It could be interesting for your project to try (for example) to see what you find when you compare the means of two groups vs the medians of two groups. Or what do you find if you do a t-test vs a MW test? etc.


## Cleaning up data

```{r read_data}
## Reading data in
raw_data <- read.csv("survey_responses.csv",nrows = 264)
```



```{r create_dictionary}
## Reassigning column names, and creating dictionary for new column names
num_questions <- ncol(raw_data)
questions <- data.frame(colnames(raw_data))
new_col_names <- paste("Q",as.character(c(1:num_questions)),sep = "")
colnames(raw_data) <- new_col_names
data_dictionary <- data.frame(cbind(questions,new_col_names))

## Save raw data with new column names to "data" which will be normalized
data <- raw_data 
```



```{r normalizing_gender}
## Normalize gender column into binary data based on whether the responder reported their gender as "Male"
gender_col <- as.character(data$Q1)
non_male <- gender_col != "Male"
gender_col[non_male] <-  "Not Male"
gender_col <- as.factor(gender_col)
data$Q1 <- gender_col
length(data$Q1)

## Add column named gender that maps Male to 1 and Not Male to 0 to be used in the logistic regression
map_gender <- function(rec) {
  if (rec == "Male") return(1) else return(0) 
}
gender <- sapply(X = data$Q1, FUN = map_gender)
data <- cbind(data,gender)
```



```{r normalizing_ethnicity}
ethnicity <- data.frame(data$Q2)
colnames(ethnicity) <- c("ethnicity_list")

ethnicity[ethnicity$ethnicity_list %in% c("Arab", "Middle Eastern"), ] <- "White"
ethnicity[ethnicity$ethnicity_list == "Black or African American, Hispanic or Latino, Multi-Racial", ] <- "Black or African American, Hispanic or Latino"
ethnicity[ethnicity$ethnicity_list == "Mixed, Jamaican/Itailian/Chinese", ] <- "Asian, Black or African American, White"
ethnicity[ethnicity$ethnicity_list %in% c("Alien", "I do not wish to declare my race/ethnicity", ""), ] <- NA
ethnicity$ethnicity_list <- droplevels(ethnicity$ethnicity_list)

## Get the right ethnic groups
ethnicity_groups <- levels(ethnicity$ethnicity_list) %>% strsplit(", ") %>% unlist %>% unique
ethnicity_groups <- ethnicity_groups[!grepl(",", ethnicity_groups)]

## Recast the ethnicity table with the comma-separated list into a new table
ethnicity <- ethnicity %>%
  rowid_to_column("id") %>%
  mutate(ethnic_group = strsplit(as.character(ethnicity_list), ", ")) %>%
  unnest() %>%
  dcast(id ~ ethnic_group)

## We get "White" and NA in the white column, for example
ethnicity[, -1] <- !is.na(ethnicity)[,-1]

## 2 new columns, non-hispanic white and only white or asian
ethnicity$"Non-Hispanic White" <- !(rowSums(ethnicity[, c("Asian", "Black or African American", "Hispanic or Latino", "Native Hawaiian or Other Pacific Islander", "NA")]) > 0)
ethnicity$"Only White or Asian" <- !(rowSums(ethnicity[, c("Black or African American", "Hispanic or Latino", "Native Hawaiian or Other Pacific Islander", "NA")]) > 0)

data <- cbind(data, ethnicity[, -1])
```



```{r normalizing_aoc}
stem_search_criteria <- c("bio", "comp sci", "compsci", "computer", "data", "natsci", "nat sci", "natural sci", "math", "chem",
                          # The fun ones:
                          "Marine Science", "Conputer Science")
data$is_stem_aoc <- stri_detect_regex(data$Q4, paste(stem_search_criteria, collapse='|'), case_insensitive=TRUE)
```



```{r order_factors, echo=FALSE}
## since most responses are on an ordinal scale, this reorders the factors so they're in the correct order (without reordering the responses are ordered alphabetically)

data$Q3 <-  factor(data$Q3,levels(data$Q3)[c(2,4,5,3,1)], ordered = TRUE)

data$Q6 <-  factor(data$Q6,levels(data$Q6)[c(2,1)], ordered = TRUE)

data$Q7 <-  factor(data$Q7,levels(data$Q7)[c(2,1,3)], ordered = TRUE)

agree_questions <- data[,8:14]
agree_questions <- catcolwise( function(my_col) factor(my_col,levels(my_col)[c(5,2,3,1,4)], ordered = TRUE))(agree_questions)
data[,8:14] <- agree_questions

average_questions <- data[,15:19]
average_questions <- catcolwise( function(my_col) factor(my_col,levels(my_col)[c(5,3,2,1,4)], ordered = TRUE))(average_questions)
data[,15:19] <- average_questions

data$Q20 <- factor(data$Q20,levels(data$Q20)[c(5,3,1,2,4)], ordered = TRUE)

data$Q22 <- factor(data$Q22,levels(data$Q22)[c(5,2,3,1,4)], ordered = TRUE)

data$Q23 <- factor(data$Q23,levels(data$Q23)[c(2,4,3,1)], ordered = TRUE)

data$Q24 <- factor(data$Q24,levels(data$Q24)[c(5,3,1,2,4)], ordered = TRUE)

data$Q25 <- factor(data$Q25,levels(data$Q25)[c(1,3,2)], ordered = TRUE)

data$Q26 <- factor(data$Q26,levels(data$Q26)[c(1,3,2)], ordered = TRUE)

```


```{r to_three_groups}
to_three_averages <- function(fctr){
  levels(fctr) <- c("Below average", "Below average", "Average", "Above average", "Above average")
  return(fctr)
}

to_three_agrees <- function(fctr){
  levels(fctr) <- c("Disagree", "Disagree", "Neutral", "Agree", "Agree")
  return(fctr)
}
```


## Contingency tables and test of association

To evaluate whether there is a connection between masculinity and confidence in mathematical ability among the New College student body, we produced crosstabs of question responses by respondents' masculine identity, and then conducted chi-squared tests of independence to evaluate whether there was an association.

In the case of question 17 ("How would you rate your mathematical ability, compared to your social group?"), we first needed to consolidate the five response groups into three (The chi-squared test assumes that each cell in the crosstab has an expected value of at least 5, and in the case of male-identifying students rating themselves well below average, the actual EV is `r sum(gender_vs_social_group_perception["Male",])*sum(gender_vs_social_group_perception[, "Well below average"])/sum(gender_vs_social_group_perception)`).

```{r crosstab_socialgroup_example, eval=FALSE}
gender_vs_social_group_perception <- table(data$Q1, data$Q17)
gender_vs_social_group_perception
```

When performing a chi-squared test of independence, we do not find a significant result. We cannot conclude that a student's gender leads to a different response on this survey question.

```{r crosstab_socialgroup_3groups}
gender_vs_social_group_perception <- table(data$Q1, to_three_averages(data$Q17))
gender_vs_social_group_perception
chisq.test(gender_vs_social_group_perception)
#mantelhaen.test(gender_vs_social_group_perception)
```

## Mann-Whitney U test
```{r mann_whitney}
get_mann_whitney <- function(ind_col, dep_col, df) {
  mw_stat <- wilcox.test(as.numeric(dep_col) ~ as.numeric(ind_col), data = df)
  return(mw_stat)
} 
```

Question 7: Are you interested in graduate school (in any discipline)?  
Possible answers: "No", "Maybe", or "Yes" 
All responses for this question were divided into two samples based on gender. One sample for all the male respondents and one sample for all of the non-male respondents.  
$H_0:$ the two samples are from the same distribution, i.e. there is significant difference between responses from male students and non-male students  
$H_a:$ the two samples are from two different distributions, i.e. there is a significant difference between responses from male students and non-male students  
The type-two error is $\alpha = .05$  

```{r q7_mann_whitney}
q7_mw_results <- get_mann_whitney(data$Q1, data$Q7, data)
q7_mw_results
```

With a p-value of 0.1708 we fail to reject the null hypothesis and conclude that there is no statistically significant difference between the responses of male students and non-male students when asked about their interest in graduate school.   


Question 23: How often are you concerned that your performance in math will confirm a negative stereotype about you?  
Possible answers: "Often", "Sometimes", "Rarely", or "Never"  
All responses for this question were divided into two samples based on gender. One sample for all the male respondents and one sample for all of the non-male respondents.  
$H_0:$ the two samples are from the same distribution, i.e. there is significant difference between responses from male students and non-male students  
$H_a:$ the two samples are from two different distributions, i.e. there is a significant difference between responses from male students and non-male students  
The type-two error is $\alpha = .05$  

```{r q23_mann_whitney}
q23_mw_results <- get_mann_whitney(data$Q1, data$Q23, data)
q23_mw_results
```

With a p-value of $2.465 \times 10^{-6}$ we reject the null hypothesis and conclude that there is a statistically significant difference between the responses of male students and non-male students when asked about the frequency of concerns that their performance in math will confirm a negative stereotype about them.  



# Appendix

## Appendix: Question breakdown
```{r plot_prep, echo=FALSE, results='hide'}
plot_data <- data

assign_ethnicity <- function(record) {
  if (sum(record) > 1) return("Muliethnic")
  if (sum(record) == 0) return("Unable to Determine")
  if (record[1] == TRUE) return("Asian")
  if (record[2] == TRUE) return("Black or African American")
  if (record[3] == TRUE) return("Hispanic or Latino")
  if (record[4] == TRUE) return("Native Hawaiian or Other Pacific Islander")
  if (record[5] == TRUE) return("White")
}
race_ethnicity_data <- data[,ethnicity_groups]

overall_race_ethnicity <- data.frame(apply(race_ethnicity_data, MARGIN = 1, FUN = assign_ethnicity))
colnames(overall_race_ethnicity) <- "Race/Ethnicity"
plot_data <- cbind(plot_data,overall_race_ethnicity)
plot_data$`Race/Ethnicity` <-  factor(plot_data$`Race/Ethnicity`,levels(plot_data$`Race/Ethnicity`)[c(5,4,1:3,6)])

plot_data$Q25 <- mapvalues(plot_data$Q25, from = levels(plot_data$Q25), to = c("No","Yes, but not at NCF","Yes, at NCF & elsewhere"))

plot_data$Q26 <- mapvalues(plot_data$Q26, from = levels(plot_data$Q26), to = c("No","Yes, but not at NCF","Yes, at NCF & elsewhere"))

plot_by_gender <- function(question_col,question_title) {
  gender_plot <- ggplot(plot_data, aes(x = Q1,fill = factor(question_col))) 
  gender_plot <- gender_plot + geom_bar(position="fill") + coord_flip()
  gender_plot <- gender_plot + xlab("Gender") + ylab("Percentage") + guides(fill=guide_legend(title=question_title))
  return(gender_plot)
}

plot_by_ethnicity <- function(question_col,question_title) {
  ethnicity_plot <- ggplot(plot_data, aes(x = `Race/Ethnicity`, fill = factor(question_col))) 
  ethnicity_plot <- ethnicity_plot + geom_bar(position="fill") + coord_flip()
  ethnicity_plot <- ethnicity_plot + ylab("Percentage") + guides(fill=guide_legend(title=question_title))
  return(ethnicity_plot)
}
```

### Question 1: What gender do you identify as?
```{r plot_q1, echo=FALSE, fig.keep='all'}
other <- (raw_data$Q1 != "Male" & raw_data$Q1 != "Female")
gender <- as.character(raw_data$Q1)
gender[other] <- "Other"
gender <- data.frame((as.factor(gender)))
colnames(gender) <- "Gender"
ggplot(gender,aes(Gender, fill = Gender)) + geom_bar() + coord_flip() + guides(fill=FALSE)
```

### Question 2: What is your race/ethnicity?
```{r plot_q2, echo=FALSE, fig.keep='all'}
plot_q2 <- ggplot(plot_data, aes(`Race/Ethnicity`, fill = `Race/Ethnicity`)) 
plot_q2 + geom_bar() + coord_flip() + guides(fill=FALSE)
```

### Question 3: What is your year at New College?
```{r plot_q3, echo=FALSE, fig.keep='all'}
plot_q3 <- ggplot(plot_data, aes(x = Q3, fill = Q3))
plot_q3 + geom_bar() + xlab('Year') + guides(fill=FALSE)
```

## Question 4: What is your Area of Concentration?
```{r plot_q4, echo=FALSE, fig.keep='all'}
q4_data <- mapvalues(plot_data$is_stem_aoc, from = c(TRUE,FALSE), to = c("STEM","Not STEM"))
q4_title <- "AOC"
plot_by_gender(q4_data,q4_title)
plot_by_ethnicity(q4_data,q4_title)
```

<!-- ## Question 5: Which math classes have you taken at New College? -->
<!-- To be included: plot describing distribution of math classes taken by the respondents, column has multiple values and need to be normalized-->

### Question 6: Are you considering, or did you ever consider a concentration in Math?
```{r plot_q6, echo=FALSE, fig.keep='all'}
q6_data <- plot_data$Q6
q6_title <- "Ever consider AOC\nin Math?"
plot_by_gender(q6_data,q6_title)
plot_by_ethnicity(q6_data,q6_title)
```

### Question 7: Are you interested in graduate school, in any discipline?
```{r plot_q7, echo=FALSE, fig.keep='all'}
q7_data <- plot_data$Q7
q7_title <- "Interested in\ngrad school?"
plot_by_gender(q7_data,q7_title)
plot_by_ethnicity(q7_data,q7_title)
```

### Question 8: "I find mathematics interesting."
```{r plot_q8, echo=FALSE, fig.keep='all'}
# l <- likert(data.frame(data$Q8),grouping=data$Q1)
# likert.bar.plot(l)
q8_data <- plot_data$Q8
q8_title <- "I find math\ninteresting."
plot_by_gender(q8_data,q8_title)
plot_by_ethnicity(q8_data,q8_title)
```

### Question 9: "Mathematics leads to many possible career opportunities."
```{r plot_q9, echo=FALSE, fig.keep='all'}
q9_data <- plot_data$Q9
q9_title <- "Math leads to many\ncareer opportunities."
plot_by_gender(q9_data,q9_title)
plot_by_ethnicity(q9_data,q9_title)
```

### Question 10: "With practice it is easy for me to improve my skills in math."
```{r plot_q10, echo=FALSE, fig.keep='all'}
q10_data <- plot_data$Q10
q10_title <- "It is easy to improve\nmy math skills with\npractice"
plot_by_gender(q10_data,q10_title)
plot_by_ethnicity(q10_data,q10_title)
```

### Question 11: "Men are generally better suited to mathematics than women."
```{r plot_q11, echo=FALSE, fig.keep='all'}
q11_data <- plot_data$Q11
q11_title <- "Men are generally\nbetter at math."
plot_by_gender(q11_data,q11_title)
plot_by_ethnicity(q11_data,q11_title)
```

### Question 12: "Many people believe that men are better suited to mathematics than women."
```{r plot_q12, echo=FALSE, fig.keep='all'}
q12_data <- plot_data$Q12
q12_title <- "Many believe that\nmen are generally\nbetter at math."
plot_by_gender(q12_data,q12_title)
plot_by_ethnicity(q12_data,q12_title)
```

### Question 13: "Some racial ethnic groups are generally better suited to mathematics than others."
```{r plot_q13, echo=FALSE, fig.keep='all'}
q13_data <- plot_data$Q13
q13_title <- "Some racial ethnic\ngroups are generally\nbetter at math."
plot_by_gender(q13_data,q13_title)
plot_by_ethnicity(q13_data,q13_title)
```

### Question 14: "Many people believe that some racial ethnic groups are better suited to mathematics than others."
```{r plot_q14, echo=FALSE, fig.keep='all'}
q14_data <- plot_data$Q14
q14_title <- "Many believe that\nsome racial ethnic\ngroups are generally\nbetter at math."
plot_by_gender(q14_data,q14_title)
plot_by_ethnicity(q14_data,q14_title)
```

### Question 15: Rate your mathematical ability compared to your high school student population.
```{r plot_q15, echo=FALSE, fig.keep='all'}
q15_data <- plot_data$Q15
q15_title <- "Rate your math skills\ncompared to your high\nschool population."
plot_by_gender(q15_data,q15_title)
plot_by_ethnicity(q15_data,q15_title)
```

### Question 16: Rate your mathematical ability compared to the student population at New College.
```{r plot_q16, echo=FALSE, fig.keep='all'}
q16_data <- plot_data$Q16
q16_title <- "Rate your math skills\ncompared to New\nCollege population."
plot_by_gender(q16_data,q16_title)
plot_by_ethnicity(q16_data,q16_title)
```

### Question 17: Rate your mathematical ability compared to your social group.
```{r plot_q17, echo=FALSE, fig.keep='all'}
q17_data <- plot_data$Q17
q17_title <- "Rate your math skills\ncompared to your\nsocial group."
plot_by_gender(q17_data,q17_title)
plot_by_ethnicity(q17_data,q17_title)
```

### Question 18: Rate your mathematical ability compared to other students of your gender.
```{r plot_q18, echo=FALSE, fig.keep='all'}
q18_data <- plot_data$Q18
q18_title <- "Rate your math skills\ncompared to students\nof your gender."
plot_by_gender(q18_data,q18_title)
plot_by_ethnicity(q18_data,q18_title)
```

### Question 19: Rate your mathematical ability compared to other students of your racial ethnic group.
```{r plot_q19, echo=FALSE, fig.keep='all'}
q19_data <- plot_data$Q19
q19_title <- "Rate your math skills\ncompared to students\nof your racial ethnic\ngroup."
plot_by_gender(q19_data,q19_title)
plot_by_ethnicity(q19_data,q19_title)
```

### Question 20: Imagine the following scenario: in the first few weeks of a math class, you have had difficulty understanding the material and completing some of the assignments. How likely are you to drop the class?
```{r plot_q20, echo=FALSE, fig.keep='all'}
q20_data <- plot_data$Q20
q20_title <- "Likelihood of dropping\na difficult math class."
plot_by_gender(q20_data,q20_title)
plot_by_ethnicity(q20_data,q20_title)
```

### Question 21: Have you ever dropped or stopped attending a math class because you believed you were not going to do well?
```{r plot_q21, echo=FALSE, fig.keep='all'}
q21_data <- plot_data$Q21
q21_title <- "Ever dropped a\ndifficult math class?"
plot_by_gender(q21_data,q21_title)
plot_by_ethnicity(q21_data,q21_title)
```

### Question 22: Compared to other subjects, do you feel more or less anxiety in mathematics classes?
```{r plot_q22, echo=FALSE, fig.keep='all'}
q22_data <- plot_data$Q22
q22_title <- "More or less anxiety\nin math classes?"
plot_by_gender(q22_data,q22_title)
plot_by_ethnicity(q22_data,q22_title)
```

### Question 23: How often are you concerned that your performance in math will confirm a negative stereotype about you?
```{r plot_q23, echo=FALSE, fig.keep='all'}
q23_data <- plot_data$Q23
q23_title <- "Frequency of concerns\nthat your math abilities\nwill confirm negative\nstereotypes?"
plot_by_gender(q23_data,q23_title)
plot_by_ethnicity(q23_data,q23_title)
```

### Question 24: Think about a typical math course you have taken at New College or imagine taking one. Did/do you feel comfortable or out of place?
```{r plot_q24, echo=FALSE, fig.keep='all'}
q24_data <- plot_data$Q24
q24_title <- "Feel comfortable\nor out of place in\nNCF math class?"
plot_by_gender(q24_data,q24_title)
plot_by_ethnicity(q24_data,q24_title)
```

### Question 25: Have you ever felt that you were perceived or treated differently in a math class due to your gender?
```{r plot_q25, echo=FALSE, fig.keep='all'}
q25_data <- plot_data$Q25
q25_title <- "Ever felt you were\ntreated differently in\nmath class due to\nyour gender?"
plot_by_gender(q25_data,q25_title) 
```

### Question 26: Have you ever felt that you were perceived or treated differently in a math class due to your race or ethnicity?
```{r plot_q26, echo=FALSE, fig.keep='all'}
q26_data <- plot_data$Q26
q26_title <- "Ever felt you were\ntreated differently in\nmath class due to\nyour race or ethnicity?"
plot_by_ethnicity(q26_data,q26_title) 
```