---
title: Does the gender and ethnicity of New College students influence their experience
  with math classes?
author: "Adriana Souza, Lydia LaSeur, Roger Filmyer"
date: "12/12/2017"
output: ioslides_presentation
---

```{r setup, include=FALSE, echo=FALSE}
knitr::opts_chunk$set(echo = FALSE)
# Loading packages we will be using
library(survey)
library(srvyr)
library(psych)
library(shiny)
library(plyr)
library(dplyr)
library(ggplot2)
library(tibble)
library(reshape2)
library(tidyr)
library(stringi)
library(likert)

## Libraries for OLR (Ordinal Logistic Regression)
library(foreign)
library(MASS)
library(Hmisc)

# load workspace from notebook
load("DiversityInMath.Rdata")
```

## Goals of the Survey
Measure the following with respect to students from underrepresented groups in math courses at NCF:  

- Belonging uncertainty  
    
- Confidence levels  
    
- Stereotype threat  
    

## Background Information
- New College has 861 students (as of Fall 2016) and the survey had a total of 264 responses which are all complete.  

- Data was de-identified before being given to us. No IRB approval, since results are not being published.

- Responders were 60% female, 28.3% male, and 11.7% non-binary. 


## Data and Cleaning {.smaller}
- **Likert item responses** 
    + Ordinal data: ordered but not translatable to continuous form
    + Strongly Disagree...Strongly Agree
    
- **Gender**
    + Male
    + Non-male
    
- **Ethnicity**
    + Non-hispanic white
    + Minorty
    
- **AOC**
    + STEM
    + Non-STEM
    

## Issues
- **Small Sample Size**: only ~260 responses
    
- **Non-response Bias**: the phenomenon that the required information is not obtained from the people selected in the sample
    
- **Social Desirability and Acquiescence Bias**: students may avoid using extreme response categories out of a desire of being perceived as having extremist views and may tend to aree with statements as presented


## Anxiety Level | Visualize Responses by Gender {.smaller}
- "Compared to other subjects, do you feel more or less anxiety in mathematics classes?"  
```{r anxiety_plot_by_gender, echo=FALSE}
plot_by_gender(q22_data,q22_title)
```


## Anxiety Level | Visualize Responses by Race/Ethnicity
```{r anxiety_plot_by_ethnicity, echo=FALSE}
plot_by_ethnicity(q22_data,q22_title)
```


## Anxiety Level | Analysis {.smaller}
```{r anxiety_analysis, echo=FALSE, results='hide'}
get_olr(anxiety_level, data)
get_mann_whitney(data$Q1, data$Q22, data)
gender_vs_anxiety_test
```
- Ordinal Logistic Regression
    + The confidence intervals for both `gender` and `is_stem` do not include 0; `is_minority` and `year` do: There is evidence to support that a student's gender and AOC are statistically significant predictors of their reported anxiety levels.

- Mann-Whitney U Test
    + p-value of 2.313 x 10^-6^ allows the rejection of the null hypothesis. Conclude that the responses from male and non-male students are from different distributions.
    
- Chi-Squared Test of Association  
    + Anxiety level responses are dependent on a student's masculinity (self-id male/non-male). p = 3.354 x 10^-05^


## Confidence Level | Visualize Responses by Gender {.smaller}
- "How would you rate your mathematical ability compared to the student population at New College?"
```{r confidence_plot_by_gender, echo=FALSE}
plot_by_gender(q16_data,q16_title)
```


## Confidence Level | Visualize Responses by Race/Ethnicity
```{r confidence_plot_by_ethnicity, echo=FALSE}
plot_by_ethnicity(q16_data,q16_title)
```


## Confidence Level | Analysis {.smaller}
```{r confidence_analysis, echo=FALSE, results='hide'}
get_olr(confidence_level, data)
get_mann_whitney(data$Q1,data$Q16,data)
gender_vs_NCF_student_perception_test
```
- Ordinal Logistic Regression
    + The confidence intervals for `gender`, `year`, and `is_stem` do not include 0; `is_minority` does: There is evidence to support that a student's gender, year, and AOC are statistically significant predictors of their reported confidence levels in mathematics classes.
    
- Mann-Whitney U Test
    + p-value of 2.278 x 10^-6^ allows the rejection of the null hypothesis. Conclude that the responses from male and non-male students are from different distributions.
    
- Chi-Squared Test of Association 
    + Students' self-reported masculinity (self-ID male/non-male) and confidence levels are associated/dependent. p = 1.604 x 10^-5^.


## Stereotype Threat | Visualize Responses by Gender {.smaller}
"How often are you concerned that your performance in math will confirm a negative stereotype about you?"
```{r stereotype_plot_by_gender, echo=FALSE}
plot_by_gender(q23_data,q23_title)
```


## Stereotype Threat | Visualize Responses by Race/Ethnicity
```{r stereotype_plot_by_ethnicity, echo=FALSE}
plot_by_ethnicity(q23_data,q23_title)
```


## Stereotype Threat | Analysis {.smaller}
```{r stereotype_analysis, echo=FALSE, results='hide'}
get_olr(stereotype_threat_felt, data)
get_mann_whitney(data$Q1,data$Q23,data)
gender_vs_stereotype_test
```
- Ordinal Logistic Regression
    + The confidence intervals for `gender`, and `is_minority` do not include 0; `year` and `is_stem`. There is evidence to support that a student's gender and ethnicity are statistically significant predictors of their reported feelings of being a target of stereotype threat in math classes.
    
- Mann-Whitney U Test
    + p-value of 2.465 x 10^-6^ allows the rejection of the null hypothesis. Conclude that the responses from male and non-male students are from different distributions.
    
- Chi-Squared Test of Association  
    + Students' self-reported masculinity and anxiety levels are associated/dependent. p = 5.758 x 10^-06^
